SecureIt: home security\\ via Android application

### 2013-01-03 relazioni/wireless/paper.tex

In order to allow the end user to select the type of monitoring and the type of alerting according to his needs about security, CPU and power consumption, a configuration panel (shown in figure ref{img:config}) is presented at each start of the application.\\

>>>>

In order to allow the end user to select the type of monitoring and the type of alerting according to his needs about security, CPU and power consumption, a configuration panel (shown in figure \ref{img:config}) is presented at each start of the application.\\
